\documentclass[10pt,a4paper]{article}
\usepackage[margin=16mm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}

\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt}
\pagenumbering{gobble}

\newcommand{\cvsection}[1]{%
  \vspace{6pt}
  {\large\bfseries #1}\\[-2pt]
  \rule{\textwidth}{0.4pt}
  \vspace{2pt}
}

\newcommand{\entry}[3]{%
  \textbf{#1} \hfill #2\\
  #3
  \vspace{2pt}
}

\begin{document}

{\LARGE \textbf{Akihiro Sakuramoto}}\\
Master's Student, AI Science Area, Japan Advanced Institute of Science and Technology (JAIST)\\
\href{mailto:s2510069@jaist.ac.jp}{s2510069@jaist.ac.jp} \quad
sakuramoto.may [at] gmail.com \quad
\href{https://github.com/aki41105}{github.com/aki41105} \quad
\href{https://orcid.org/0009-0006-7932-0219}{ORCID: 0009-0006-7932-0219}\\
\href{https://www.linkedin.com/in/%E6%99%83%E5%BC%98-%E6%AB%BB%E6%9C%AC-37024b328/}{LinkedIn} \quad
\href{https://www.jaist.ac.jp/~okada-s/index.html}{Okada Laboratory}

\cvsection{Research Overview}
I study real-world human-robot interaction through social signal processing and multimodal interaction, focusing on how people and robots relate to one another in everyday settings.

\cvsection{Education}
\entry{Japan Advanced Institute of Science and Technology (JAIST)}{Apr. 2025--Present}
{M.S. student, AI Science Area}

\entry{University of Toyama}{Apr. 2021--Mar. 2025}
{B.E., Electrical and Electronic Engineering Course, Faculty of Engineering}

\cvsection{Experience and Activities}
\entry{Joint Research with CyberAgent AI Lab}{2025--Present}
{Research on real-world HRI and interaction quality evaluation using in-store customer-service robot interaction data.}

\entry{Internship, FUJI Corporation}{Aug. 2025--Sep. 2025}
{Worked on AI-based image inspection for defects occurring inside solder paste printers, including data collection and algorithm development.}

\entry{Internship, Robot Learning Laboratory, NAIST}{Feb. 2024--Mar. 2024}
{Worked on robot manipulation tasks using reinforcement learning.}

\entry{NHK Student Robocon 2023 Finalist}{2023}
{Worked on robot control in the University of Toyama Robocon Project using ROS, C, and Python.}

\cvsection{Publications and Presentations}
\begin{itemize}
  \item Sakuramoto A., Hayashi T., Miyoshi R., Okafuji Y., Okada S. \textit{A Multimodal Rapport Estimation Model for Evaluating Interaction Quality in Real-World HRI}. Meeting on Image Recognition and Understanding (MIRU), Poster presentation, Aug. 2026.
\end{itemize}

\cvsection{Awards}
\begin{itemize}
  \item JAIST Student Grant Scholarship, awarded for academic excellence, 2025--2026.
\end{itemize}

\cvsection{Skills}
\begin{itemize}
  \item Research areas: human-robot interaction, social signal processing, multimodal interaction, interaction quality evaluation.
  \item Technical experience: Python, C, ROS, data collection, annotation, machine learning, reinforcement learning.
\end{itemize}

\end{document}
